---
title: "`r params$title`"
params:
  #title: "Custom Report"
  title: "Test Report"
  #technology: "Cross Flow"
  technology: "Ocean Current"
  # aoi_wkt: "POLYGON ((-67.06819 44.99416, -67.1857 44.94707, -67.21651 44.88058, -67.15834 44.78871, -67.04385 44.81789, -66.91015 44.86279, -67.06819 44.99416))"
  aoi_wkt: "POLYGON ((-68.37953 44.857, -67.38415 43.89608, -64.21114 45.0997, -64.90587 45.89335, -68.37953 44.857))"
  stressors: 
    # - Noise
    # - EMF
    - Noise
  receptors:
    # - Marine Mammals
    # - Fish
    - Cetaceans
    - Pinnipeds
  stressor_receptors:
    # - Marine Mammals AND Noise
    # - Fish AND EMF
    - Cetaceans AND Noise
    - Pinnipeds AND Noise
  lit_tethys: true
  lit_ferc: false
  spatial: true
  mgt_tethys: false
output:
  pdf_document:
    toc: true
    toc_depth: 4
    number_sections: true
    #keep_md: yes
    #latex_engine: xelatex
  word_document:
    toc: true
    toc_depth: 4
    number_sections: true
    #keep_md: yes
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true
    mathjax: null
editor_options: 
  chunk_output_type: console
always_allow_html: true
---

```{r setup, include=F}
# render("report_template.Rmd", output_file="report_template.pdf", output_format="pdf_document")
# render("report_template.Rmd", output_file="report_template.docx", output_format="word_document")
# render("report_template.Rmd", output_file="report_template.html", output_format="html_document")
knitr::opts_chunk$set(echo = F, warning = F, message = F, eval = T)
```

```{r init}
source(here::here("functions.R")) # libraries, db connection object (con)
# rmd_params <- readRDS(here("data/tmp_rmd_params.rds"))
```

# Configuration

```{r}
# params = list(technology="Cross Flow")
#tech_choices <- read_csv(here("report/data/tech_choices.csv"))
# TODO: integrate finer detail in tech_choices.csv with tags.csv
tech <- read_csv(here("data/tags.csv")) %>% 
  filter(facet == "technology") %>% 
  select(tag = item_label, tag_parent, tag_img) %>% 
  filter(tag == params$technology) %>% 
  mutate(
    img_local = map_chr(
      tag_img, 
      function(url){
        # url <- tech$tag_img
        fname         <- urltools::path(url) %>% url_decode() %>% basename()
        img_local <- file.path(here("report/data/tech_images"), fname)
        if (!file.exists(img_local))
          download.file(url, img_local)
        img_local}))

stopifnot(nrow(tech) == 1)

bullets <- function(tags, indent=1){
  glue("{strrep(' ', indent*2)}- {tags}", .trim = F) %>% 
  paste(collapse = "\n") %>% 
  cat()
}
```

## Technology: `r glue("{params$technology}")`

![](`r ifelse(knitr::is_html_output(), tech$tag_img, tech$img_local)`)

## Stressors & Receptors

* Stressors

```{r, results='asis'}
bullets(params$stressors)
```

* Receptors

```{r, results='asis'}
bullets(params$receptors)
```

* Stressor-Receptors

```{r, results='asis'}
bullets(params$stressor_receptors)
```

## Location

```{r map}
# params = list(aoi_wkt = "POLYGON ((-67.06819 44.99416, -67.1857 44.94707, -67.21651 44.88058, -67.15834 44.78871, -67.04385 44.81789, -66.91015 44.86279, -67.06819 44.99416))")

aoi_sf <- tibble(
  geometry = params$aoi_wkt) %>%
  st_as_sf(wkt = "geometry", crs=4326)

# TODO: inset map showing larger area
leaflet(
  options = leafletOptions(
    zoomControl = F,
    attributionControl = F)) %>%
  addProviderTiles(providers$Esri.OceanBasemap) %>%
  addPolygons(data = aoi_sf)
```

# Literature

## Stressors

Stressors are potentially harmful environmental effects from technology for marine renewable energy.

```{r stressors, results='asis'}
# params = list(stressors = c("Noise", "EMF"))
if (params$lit_tethys)
  knit_tethys_literature_from_tags(params$stressors)
```

## Receptors

Receptors are species, habitats and human activities of environmental concern.

```{r receptors, results='asis'}
# params = list(receptors = c("Marine Mammals", "Fish"))
if (params$lit_tethys)
  knit_tethys_literature_from_tags(params$receptors)
```

## Stressor-Receptors

```{r stressor_receptors, results='asis'}
# params = list(stressor_receptors = c("Marine Mammals AND Noise", "Fish AND EMF"))
if (params$lit_tethys)
  knit_tethys_literature_from_tags(params$stressor_receptors)
```

# Spatial

Spatial data of Receptors are extracted for the Location from datasets harvested predominantly from [MarineCadastre.gov](https://MarineCadastre.gov).

```{r, results='asis'}
# datasets_gsheet2db ----
# datasets_marinecadastre.gov.csv - Google Sheet
#   edit online: https://docs.google.com/spreadsheets/d/1MMVqPr39R5gAyZdY2iJIkkIdYqgEBJYQeGqDk1z-RKQ/edit#gid=0
# datasets_gsheet2db()

# params = list(
#   receptors = c("Marine Mammals", "Fish"),
#   aoi_wkt = "POLYGON ((-67.06819 44.99416, -67.1857 44.94707, -67.21651 44.88058, -67.15834 44.78871, -67.04385 44.81789, -66.91015 44.86279, -67.06819 44.99416))")

if (params$spatial){
  datasets <- tbl(con, "datasets") %>% 
    collect() %>%
    replace_na(list(buffer_km = 0)) %>% 
    select(-notes, -issues) %>% 
    separate_rows(tags, sep = ";") %>% 
    rename(tag = tags) %>% 
    filter(
      tag %in% params$receptors) %>% 
    arrange(tag, title)
  
  lapply(1:nrow(datasets), function(i_datasets) {
    knit_expand('_spatial-tag-dataset.Rmd') }) %>% 
    knit_child(text = unlist(.), quiet = T) %>% 
    cat(sep = '\n\n')
}
```
