---
title: "Spatial Summaries"
output: 
  html_document:
    toc: true
    number_sections: false
editor_options: 
  chunk_output_type: console
---


```{r setup, include=F}
if (!require(librarian)){
  remotes::install_github("DesiQuintans/librarian")
  library(librarian)
}
shelf(
  # database
  DBI, RPostgres,
  # spatial
  ggmap, leaflet,
  r-spatial/mapview, # https://github.com/r-spatial/mapview/issues/324
  sf, sp,
  # scrape
  # rvest, 
  # tidyverse
  dplyr, purrr, readr, tibble, tidyr,
  # someday
  # googledrive, zeallot,
  # report
  DT, gt, htmltools, htmlwidgets, kableExtra, knitr, markdown, rmarkdown, shiny, webshot,
  # utility
  fs, glue, here, png, scales, stringr, urltools
)
here <- here::here

pass <- readLines("../password_mhk-env.us")
con = dbConnect(
  RPostgres::Postgres(),
  dbname   = "gis",
  host     = "marineenergy.app",
  port     = 5432,
  user     = "admin",
  password = pass
)

knitr::opts_chunk$set(echo = T, warning = F, message = F) #, connection = "db")
```

# About

This document is designed to test and track marine energy data summarization efforts for the [marineenrgy.app](https://marineenergy.app/).
Raw data sources have been loaded into a PostgreSQL database and our task is to interpret and summarize the *important* information.

Once tested, data queries and metadata get compiled into a [master table](https://docs.google.com/spreadsheets/d/1MMVqPr39R5gAyZdY2iJIkkIdYqgEBJYQeGqDk1z-RKQ/edit#gid=936111013), which are then ingested by `tabulate_dataset_shp_within_aoi` in [marineenergy/apps/functions.R](https://github.com/marineenergy/apps/blob/c98a3bacfa06370e823863f52b6633036cd228dc/functions.R).

Some notes related to this effort [here](https://docs.google.com/document/d/109KwZ2PsKkD_ohRZI5F3IkIEOmYKXLl-qVf_ZxHIoyo).

---


# Data Summary Testing Functions

## Existing Data Summaries

Usage: `test_tabulate_dataset_shp_within_aoi(<dataset code>, <aoi size>, <optional: coast>)`

Example: `test_tabulate_dataset_shp_within_aoi("ocs-lease-blk", "S", "W")`

or: `test_tabulate_dataset_shp_within_aoi("ocs-lease-blk", "L")`

```{r test_existing_sql, class.source='fold-show'}
# source("functions.R")

test_tabulate_dataset_shp_within_aoi <- function(ds_code, aoi_size, coast){
  # AOI covering most of North America
  if (aoi_size == "L") {
    aoi_wkt = "POLYGON ((
      -149.765625 9.795677582829743, 
      -37.96875 9.795677582829743, 
      -37.96875 56.9449741808516, 
      -149.765625 56.9449741808516, 
      -149.765625 9.795677582829743))"
  # AOI covering the United States
  } else if (aoi_size == "M") {
    aoi_wkt = "POLYGON ((
      -131.484375 26.43122806450644, 
      -66.796875 26.43122806450644, 
      -66.796875 49.83798245308484, 
      -131.484375 49.83798245308484, 
      -131.484375 26.43122806450644))"
  # AOI covering the U.S. east or west coast
  } else {
    if (missing(coast)) {
      aoi_wkt = "POLYGON ((
        -83.3203125 30.90222470517144, 
        -80.33203125 25.64152637306577, 
        -61.52343749999999 44.96479793033101, 
        -72.94921875 45.213003555993964, 
        -83.3203125 30.90222470517144))"
    } else {
      if (coast == "W") {
        aoi_wkt = "POLYGON ((
          -128.84765625 32.99023555965106, 
          -118.30078125 32.99023555965106, 
          -118.30078125 45.460130637921004, 
          -128.84765625 45.460130637921004, 
          -128.84765625 32.99023555965106))"
      } else {
        aoi_wkt = "POLYGON ((
          -83.3203125 30.90222470517144, 
          -80.33203125 25.64152637306577, 
          -61.52343749999999 44.96479793033101, 
          -72.94921875 45.213003555993964, 
          -83.3203125 30.90222470517144))"
      }
    }
  }
  
  dataset_code = ds_code; aoi_wkt = aoi_wkt; output = "kable"
  res <- tabulate_dataset_shp_within_aoi(ds_code, aoi_wkt)
  return(res)
}
```


## New Data Summaries

Usage: `test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, aoi_size)`
```{r test_new_sql, class.source='fold-show'}
test_new_summary <- function(select_sql, summarize_sql, buffer_nm, intersection, aoi_size, coast) {
  if (aoi_size == "L") {
    aoi_wkt = "POLYGON ((
      -149.765625 9.795677582829743, 
      -37.96875 9.795677582829743, 
      -37.96875 56.9449741808516, 
      -149.765625 56.9449741808516, 
      -149.765625 9.795677582829743))"
  # AOI covering the United States
  } else if (aoi_size == "M") {
    aoi_wkt = "POLYGON ((
      -131.484375 26.43122806450644, 
      -66.796875 26.43122806450644, 
      -66.796875 49.83798245308484, 
      -131.484375 49.83798245308484, 
      -131.484375 26.43122806450644))"
  # AOI covering the U.S. east or west coast
  } else {
    if (missing(coast)) {
      aoi_wkt = "POLYGON ((
        -83.3203125 30.90222470517144,
        -80.33203125 25.64152637306577,
        -61.52343749999999 44.96479793033101,
        -72.94921875 45.213003555993964,
        -83.3203125 30.90222470517144))"
    } else {
      if (coast == "W") {
        aoi_wkt = "POLYGON ((
          -128.84765625 32.99023555965106, 
          -118.30078125 32.99023555965106, 
          -118.30078125 45.460130637921004, 
          -128.84765625 45.460130637921004, 
          -128.84765625 32.99023555965106))"
      } else {
        aoi_wkt = "POLYGON ((
          -83.3203125 30.90222470517144, 
          -80.33203125 25.64152637306577, 
          -61.52343749999999 44.96479793033101, 
          -72.94921875 45.213003555993964, 
          -83.3203125 30.90222470517144))"
      }
    }
  }
  
  
  if (length(aoi_wkt) > 1){
    aoi_wkts <- glue("'SRID=4326;{aoi_wkt}'::geometry")
    aoi_sql  <- glue("ST_COLLECT(\n{paste(aoi_wkts, collapse=',\n')})") # Is this recreating the ST_COLLECT statement
  } else {
    aoi_sql <- glue("'SRID=4326;{aoi_wkt}'::geometry")
  }
  
  # Different set of queries required for data sets that do or
  #   do not need area weighted statistics. 
  # This is controlled by the "st_intersection" field in the "datasets" table
  if (intersection){
    # Area weighted statistics ARE required
    ixn_sql <- str_replace(select_sql, 'geometry', 'geometry, st_intersection(ds.geometry, buf_aoi.geom) as ixn ')
    
    # Check if there is a sql summary statement for this dataset
    if (!is.na(summarize_sql)){
      x_df <- dbGetQuery(
        con,
        glue("
          with
            buf_aoi as (
              select ST_BUFFER({aoi_sql}, {buffer_nm} * 1852) as geom),
            tmp_aoi as (
              {ixn_sql} as ds, buf_aoi
              where st_intersects(ds.geometry, buf_aoi.geom))
            {summarize_sql}
          "))
    } else {
      x_sf <- st_read(
        con, 
        glue("
          with
            buf_aoi as (
              select ST_BUFFER({aoi_sql}, {buffer_nm} * 1852) as geom)
            {ixn_sql} as ds, buf_aoi
            where st_intersects(ds.geometry, buf_aoi.geom)
          "))
      x_df <- st_drop_geometry(x_sf)
    }
    
  } else {
    # Area weighted statistics NOT required
    if (!is.na(summarize_sql)){
      x_df <- dbGetQuery(
        con, glue("
          with 
            buf_aoi as (
              select ST_BUFFER({aoi_sql}, {buffer_nm} * 1852) as geom ),
            tmp_aoi as (
              {select_sql} as ds
              inner join buf_aoi on st_intersects(ds.geometry, buf_aoi.geom) )
           {summarize_sql}
           "))
    } else {
      x_sf <- st_read(
        con, query = glue("
          with 
            buf_aoi as (
              select ST_BUFFER({aoi_sql}, {buffer_nm} * 1852) as geom)
            {select_sql} as ds
            inner join buf_aoi on st_intersects(ds.geometry, buf_aoi.geom )
            "))
      x_df <- st_drop_geometry(x_sf)
    }
  }
  
  return(datatable(x_df, rownames=F))
}
```

---

# Data Summaries

## Template
```{r template, eval=F, class.source='fold-show'}
select_sql <- glue('')

summarize_sql <- glue("")

intersection = F
buffer_nm = 0
aoi_size = "M"
coast = "E"

test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, aoi_size, coast)
```

---

## Selected Pipelines
```{r pipelines, class.source='fold-show'}
select_sql <- glue('
  select
    fed_seg_len_ft,
    status_code,
    outer_diameter,
    product_code,
    aprv_code,
    operator,
    geometry
  from (
    select
      seg_length as fed_seg_len_ft,
      status_cod as status_code,
      ppl_size_c as outer_diameter,
      prod_code as product_code,
      aprv_code,
      sde_compan as operator,
      geometry
    from shp_ppl_arcs
    UNION
    select
      seg_length as fed_seg_len_ft,
      status_cod as status_code,
      ppl_size_c as outer_diameter,
      prod_code as product_code,
      aprv_code,
      sde_compan as operator,
      geometry
    from "shp_BOEM_Pacific_Pipelines_2011-08_nad83")')

summarize_sql <- glue("
  select
    status_code as \"Status Code\",
    product_code as \"Product Code\",
    operator as \"Operator\",
    to_char(round(sum(st_length(ixn::geography)) * 3.281), 'FM999,999,999') as \"Segment Length (ft)\"
  from 
    tmp_aoi
  group by
    status_code, product_code, operator
  order by
    status_code, product_code, operator")

intersection = T
buffer_nm = 0

test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, "M")
```


## Outer Continental Shelf Proposed Final Program Areas 2017-2022
```{r ocs-programs, class.source='fold-show'}
select_sql <- glue('
  select
  	notes, geometry
  from (
  	select 
  	  notes, geometry
  	from 
  	  "shp_GOMR_Proposed_FInal_Program_Area"
  	UNION
  	select 
  	  notes, geometry 
  	from 
      "shp_Alaska_Region_2017-2022_Proposed_Final_Program_Area")')

summarize_sql <- glue("
  select
    replace(notes, 'FInal', 'Final') as \"Note\",
    round(100 * sum(st_area(ixn::geography) / st_area(geometry::geography))) || ' %' as \"AOI Overlap\"
  from
    tmp_aoi
  group by
    notes
  order by
    notes
")

intersection = T
buffer_nm = 0

test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, "M")
```


## Federal Outer Continental Shelf (OCS) Sand and Gravel Borrow Areas (Lease Areas)
```{r fed-ocs-lease, class.source='fold-show'}
select_sql <- glue('
  select
    state,
    leaseno,
    projectid,
    projectcou,
    totalsanda,
    fiscalyear,
    effectived,
    expiration,
    originalvo,
    borrowarea,
    amendmentd,
    amendmentn,
    additional,
    acres,
    leasestatu,
    geometry
  from "shp_Leases_200203"
')

summarize_sql <- glue("
  select
    state as \"State\",
    leaseno as \"Lease\",
    projectid as \"Project\",
    leasestatu as \"Status\",
    expiration as \"Expiration\",
    totalsanda as \"Allocated Sand Volume (yd^3)\"
  from
    tmp_aoi
  order by
    state, leasestatu, expiration, leaseno, projectid
")

intersection = F
buffer_nm = 0

test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, "M")
```


## Coastal Barrier Resources System
```{r cbrs, class.source='fold-show'}
select_sql <- glue('
  select
    unit,
    name,
    unit_type,
    fast_acres,
    wet_acres,
    shore_mile,
    geometry
  from "shp_CBRS_Polygons_03122019"
')

summarize_sql <- glue("
  select
    unit as \"CBRS Unit\",
    name as \"Unit Name\",
    unit_type as \"Unit Type\",
    round(fast_acres * sum(st_area(ixn::geography) / st_area(geometry::geography))) as \"Upland Area (acres)\",
    round(wet_acres * sum(st_area(ixn::geography) / st_area(geometry::geography))) as \"Wetland Area (acres)\"
  from
    tmp_aoi
  group by
    unit, name, unit_type, fast_acres, wet_acres
  order by
    unit, name, unit_type
")

intersection = T
buffer_nm = 0.00329158
aoi_size = "S"
coast = "E"
  
test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, aoi_size, coast)
```


## National Seafloor Geology (GLORIA)

Overkill?

> to_char(round(sum(st_area(geometry::geography) * (st_area(ixn::geography) / st_area(geometry::geography))) / 1000), 'FM999,999,999,999') as "Area (km^2)"
    
```{r gloria, eval=T, class.source='fold-show'}
select_sql <- glue('
  select
    unit, 
    description, 
    geometry 
  from (
    select area, unit, null as description, geometry from shp_interp
    union
    select area, unit, descriptio as description, geometry from shp_west
    union
    select st_area(geometry) as area, tunits as unit, null as description, geometry from shp_geo_poly
    union
    select area, geoabrv as unit, descriptio as description, geometry from shp_geology
  )
')

summarize_sql <- glue("
  select
    unit as \"Unit\",
    case when description is null then 'No description' when description = 'No Data' then 'No description' else description end as \"Description\"
  from 
    tmp_aoi
  where
    unit is not null and unit != 'nodat'
  group by
    unit, description
  order by
    unit, description
")

intersection = F
buffer_nm = 0
aoi_size = "M"
coast = "E"

test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, aoi_size, coast)
```


## EFH Areas Protected from Fishing
```{r nationwide-efha, eval=T, class.source='fold-show'}
select_sql <- glue('
  select 
  	fmc_report,
  	sitename_l,
  	instatewat,
  	lifestage,
  	lttdt_link,
  	acres,
  	geometry
  from shp_nationwide_efha
')

summarize_sql <- glue("
  select
    fmc_report as \"FMC Region\",
    sitename_l as \"Site\",
    case when instatewat = 'Y' then 'Yes' else 'No' end as \"State Waters\",
    lifestage as \"Lifestage\",
    to_char(round(sum(st_area(geometry::geography) * (st_area(ixn::geography) / st_area(geometry::geography))) / 4047), 'FM999,999,999,999') as \"Acres\"
  from
    tmp_aoi
  group by
    fmc_report, sitename_l, instatewat, lifestage, lttdt_link
  order by
    fmc_report, sitename_l, instatewat, lifestage, lttdt_link
")

intersection = T
buffer_nm = 0
aoi_size = "S"
coast = "W"

test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, aoi_size, coast)
```


## Ocean Wave Resource Potential

wef = wave energy flux (kilowatts per meter of wave crest)

depth = meters

Could go about summarizing this in a few different ways. Lots of points.

```{r wave-power, eval=F, class.source='fold-show'}
select_sql <- glue('
  select
    depth_wef,
    ann_wef,
    geometry
  from
    shp_wave_power_density
')

summarize_sql <- glue("
  select
    depth_wef,
    avg(ann_wef) as avg_ann_wef
  from
    tmp_aoi
  group by
    depth_wef
  order by
    depth_wef
")

intersection = F
buffer_nm = 0
aoi_size = "S"
coast = "E"

test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, aoi_size, coast)
```


## Coastal Maintained Channels

Native geometry is in 3D (MultiPolygon Z)

Interesting problem when forcing geometry to 2D:

- Using `ST_Force2D(geometry)` and `intersection = Y` causes query function to fail.
- Query function looks for `geometry` in the `select_sql` string and replaces it with `geometry, st_intersection(...)`
- Workaround was to use `ST_Force2D(geom)`, which I assume is just shorthand for `geometry`. Not sure why it works, but it does.

Sparse metadata for this dataset. Not sure what columns mean.

```{r coastal-channels, eval=T, class.source='fold-show'}
select_sql <- glue('
  select
  	objnam,
  	themelayer,
  	inform,
  	drval1,
  	quasou,
  	quasou_txt,
  	sordat,
  	fairway,
  	dsnm,
  	dataaccess,
  	datatype,
  	st_force2d(geom) as geometry
  from shp_maintainedchannels
')

summarize_sql <- glue("
  select
    themelayer as \"Category\",
    fairway as \"Fairway\",
    quasou_txt \"Quality\",
    inform as \"Notes\"
  from
    tmp_aoi
  where 
    fairway is not null
  group by
    themelayer, fairway, inform, quasou_txt
")

intersection = T
buffer_nm = 0
aoi_size = "S"
coast = "W"

test_new_summary(select_sql, summarize_sql, buffer_nm, intersection, aoi_size, coast)
```